\textls[-0]{\thetitle}

### 2023-03-04 related-work.tex
Rephrasing, less confusing.

\citet{forsta2020} introduce \emph{Coq à la carte}.
It still follows DTC, but rather than embracing DTC's use of generic
fixed points, it considers specific instantiations instead.
The resulting mechanism appears more streamlined than prior \emph{à la
carte} approaches particularly for its extensive tool support for generating boilerplate code.
%
But even with the tool support, components (e.g., "substlem") of
individually developed feature extensions have to be composed separately
by invoking the tool. Alternatively, \citet{vdr2022intrinsically} uses 
containers and signature to mechanize intrinsically-typed target language. 
Combined with Agda's advanced unification mechanism, the authors get rid of 
a large number of boilerplate code. 
%
%The approach does not seem to fully address the expression problem,
%as \citet{liwei2022} observe, in that further extending a composed
%mechanization causes (a small amount of) boilerplate code that glues definitions
%to be regenerated.

>>>>

\citet{forsta2020} introduce \emph{Coq à la carte}.
It still follows DTC, but rather than embracing DTC's use of generic
fixed points, it considers specific instantiations instead.
The resulting mechanism appears more streamlined than prior \emph{à la
carte} approaches particularly for its extensive tool support for generating boilerplate code.
%
But even with the tool support, components (e.g., "substlem") of
individually developed feature extensions have to be composed separately
by invoking the tool. \citet{vdr2022intrinsically} mechanize intrinsically-typed
target language based on container and signature\cite{morris2009indexed}. 
Thanks to the nature of intrinsically-typed abstract syntax trees (ASTs) and Agda's advanced unification mechanism, the authors were able to eliminate a significant amount of code that dealt with "impossible" cases.
%
%The approach does not seem to fully address the expression problem,
%as \citet{liwei2022} observe, in that further extending a composed
%mechanization causes (a small amount of) boilerplate code that glues definitions
%to be regenerated.
